%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Analysis Scientific Research} % Job title
    {CEFET/RJ} % Organization
    {Rio de Janeiro, Brazil} % Location
    {Aug. 2020 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an AI model to recognize human emotion with text analysis.}
        \item {Helped teacher with tasks.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fullstack Developer} % Job title
    {CEFET/RJ} % Organization
    {Rio de Janeiro, Brazil} % Location
    {Feb. 2024 - Feb. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a web software for KYC validation, ensuring user security and compliance by registering their data on a smart contract in the Ethereum blockchain.}
        \item {Structured a scalable and modular backend using TypeScript, NestJS, and Prisma, following Clean Architecture principles for better maintainability.}
        \item {Implemented secure authentication with JWT for access control in both frontend and backend.}
        \item {Developed the connection between the backend and blockchain using Ethers.js, enabling secure and efficient interactions with the smart contract.}
        \item {Managed development and production environments with Docker, ensuring easy deployment and system standardization.}
        \item {Applied Zod for schema validation and environment variable configuration, preventing errors and ensuring data consistency.}
        \item {Utilized the Serpro Datavalid API for facial recognition and document verification, enhancing accuracy in KYC validation.}
        \item {Created a responsive and intuitive interface using Next.js, Tailwind CSS, Radix UI, and Lucid React, applying hooks and useContext for state management.}
        \item {Implemented communication between frontend and backend using Axios, ensuring efficient and secure requests.}
        \item {Deployed the frontend using Cloudflare Pages and the backend with Render, ensuring a scalable, reliable, and globally accessible infrastructure.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fullstack Developer} % Job title
    {Drip Too Hard} % Organization
    {Remote} % Location
    {Sep. 2024 - May 2026} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a fashion social network for web and mobile where users create, share and favorite outfits, with automatic background removal on garment photos.}
        \item {Architected a modular and scalable backend with NestJS, TypeScript and Prisma over PostgreSQL, following Clean Architecture and DDD with isolated use cases, repositories and domain entities.}
        \item {Developed a Python background-removal microservice (rembg) to deliver clean, isolated garment images.}
        \item {Integrated AWS S3 with presigned URLs for image storage and AWS Rekognition for image moderation, optimizing processing with Sharp.}
        \item {Implemented authentication and authorization with AWS Cognito (OAuth) and JWT, enforcing role-based access control across backend and clients.}
        \item {Built the web client with Next.js (App Router), React, TypeScript, Tailwind CSS and NextAuth, with form validation via React Hook Form and Zod.}
        \item {Developed the mobile app with React Native and Expo (EAS Build/Submit), React Navigation and Expo SecureStore for secure session handling.}
        \item {Provisioned the entire AWS infrastructure as code with Terraform (VPC, ECS, ECR, ALB, RDS with RDS Proxy, CloudFront, Secrets Manager, IAM) across staging and production.}
        \item {Automated CI/CD with GitHub Actions for backend, frontend, database migrations, mobile releases and Terraform plan/apply, containerizing services with Docker.}
        \item {Ensured quality with unit, integration and end-to-end tests using Jest, Supertest and Playwright.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {RSM} % Organization
    {Remote} % Location
    {Mar. 2026 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing web applications with React, building responsive, component-driven interfaces.}
        \item {Developing cross-platform mobile applications with React Native for iOS and Android.}
        \item {Working in an agile workflow, tracking tasks and sprints on Azure Boards.}
        \item {Collaborating with the team to deliver and maintain reusable UI components and features.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
